My title

### 2024-03-11 paper/paper.qmd
Update paper.qmd

# Introduction
The goal of the Cooperative Election Study (CES) is to investigate how Americans vote and perceive their electoral experiences, how they hold their representatives accountable in elections, and how their behavior and experiences vary depending on the political climate and social milieu. The study used an extremely large sample that allowed it to account for variations across different legislative districts. Actually, the sample size at the state level is sufficient to measure the voter preference distribution within the majority of states with a respectable degree of accuracy.
60 teams participated in 2022CES, which resulted in a 60,000-case generic content sample. 
Fall of 2022 saw the recruitment of study participants. Every research team invested in a 1,000-person nationwide sample survey from Redwood City, California-based YouGov. Two waves of interviewing were used for the 2022 survey. Pre-election surveys were filled out on the spot between September 29 and November 8. The post-election campaigning frenzy took place between November 10 and December 15. For every 1,000 respondents, half of the questions had common material while the other half were fully created and managed by each study team. Questions that are common to all team modules and have a sample size equal to the total sample size of all team modules make up common content. Every one of the sixty teams bought a 1,000-person survey. Every case was chosen online, and YouGov created a corresponding random sample for this investigation.
The first data release happened on March 20, 2023. The Harvard University database contains archived and accessible data from this investigation. Vote verification is included in data release 2 for all respondents.
The study on CES 2022 is still under progress. Using a large-scale national survey, the Collaborative Congressional Election project was founded in 2006 to investigate congressional elections and representation. The project built upon the analysis conducted by the Public Opinion Research and Training Lab at the Massachusetts Institute of Technology in 2005.
# Data {#sec-data}

### Source and Methodology
The 2022 Cooperative Election Study (CES) (@main_data) involved significant data preprocessing, cleaning, and labeling efforts to ensure the quality and representativeness of the survey data. These efforts are elaborated on through descriptions of sampling methodology, matching procedures, and weighting processes as outlined in the CES Guide 2022.

>>>>

# Introduction
The goal of the Cooperative Election Study (CES) is to investigate how Americans vote and perceive their electoral experiences, how they hold their representatives accountable in elections, and how their behavior and experiences vary depending on the political climate and social milieu. The study used an extremely large sample that allowed it to account for variations across different legislative districts. Actually, the sample size at the state level is sufficient to measure the voter preference distribution within the majority of states with a respectable degree of accuracy.
60 teams participated in 2022CES, which resulted in a 60,000-case generic content sample. 
Fall of 2022 saw the recruitment of study participants. Every research team invested in a 1,000-person nationwide sample survey from Redwood City, California-based YouGov. Two waves of interviewing were used for the 2022 survey. Pre-election surveys were filled out on the spot between September 29 and November 8. The post-election campaigning frenzy took place between November 10 and December 15. For every 1,000 respondents, half of the questions had common material while the other half were fully created and managed by each study team. Questions that are common to all team modules and have a sample size equal to the total sample size of all team modules make up common content. Every one of the sixty teams bought a 1,000-person survey. Every case was chosen online, and YouGov created a corresponding random sample for this investigation.
The first data release happened on March 20, 2023. The Harvard University database contains archived and accessible data from this investigation. Vote verification is included in data release 2 for all respondents.
The study on CES 2022 is still under progress. Using a large-scale national survey, the Collaborative Congressional Election project was founded in 2006 to investigate congressional elections and representation. The project built upon the analysis conducted by the Public Opinion Research and Training Lab at the Massachusetts Institute of Technology in 2005.

# Data {#sec-data}

## Source and Methodology
The 2022 Cooperative Election Study (CES) (@main_data) involved significant data preprocessing, cleaning, and labeling efforts to ensure the quality and representativeness of the survey data. These efforts are elaborated on through descriptions of sampling methodology, matching procedures, and weighting processes as outlined in the CES Guide 2022.
